### 2013-10-14 inst/examples/sensitivity-ricker.Rmd
new sensitivity files

```{r stateeq-local}
f <- Myers

@@

```{r sdp-pars, dependson="stateeq-local"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1
x_grid <- seq(0, 1.5 * 6, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <-  1.7 # observations start from
x0 <- 5 # simulation under policy starts from
Tobs <- 40
MaxT = 1000 # timeout for value iteration convergence
seed <- round(runif(32) * 1e6)
seed[1] <- 1234
seed
```

@@

  p <- c(1.5 + rnorm(1, 0, .1), 2.5 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .2))

>>>>

```{r stateeq-local}
f <- RickerAllee

@@

```{r sdp-pars, dependson="stateeq-local"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1
x_grid <- seq(0, 1.5 * 8, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <-  5.7 # observations start from
x0 <- 8 # simulation under policy starts from
Tobs <- 40
MaxT = 1000 # timeout for value iteration convergence
seed <- round(runif(32) * 1e6)
seed[1] <- 1234
seed
```

@@

  p <- c(2 + rnorm(1, 0, .1), 8 + rnorm(1, 0, .1), 5 + rnorm(1, 0, .2))
